Histograms

### 2021-06-11 analysis/histograms.Rmd
feat: use imputed data

```{r histograms_setup}
library("targets")
tar_load(raw_data)

.hist <- function(
    ..., xlab = deparse(substitute(x)), main = paste("Histogram of", xlab),
    col = palette.colors(2L)[2]
)hist(..., main = main, xlab = xlab, col = col)
```

@@

```{r histograms_age}
.hist(raw_data$Age, xlab = "Age")
```

# Laboratory Measurements

```{r histograms_labs, results = "asis", message = FALSE, warning = FALSE}
labv <- sort(grep("_[SECQ]$", colnames(raw_data), value = TRUE))

for (v in labv) {
    cat("\n\n##", v , "\n\n")
    .hist(raw_data[[v]], main = paste0("Histogram of ", v), xlab = v)
}
```

>>>>

```{r histograms_setup}
library("targets")
tar_load(imp_data)

.hist <- function(
    ..., xlab = deparse(substitute(x)), main = paste("Histogram of", xlab),
    col = palette.colors(2L)[2L]
)hist(..., main = main, xlab = xlab, col = col)
```

@@

```{r histograms_age}
.hist(imp_data$Age, xlab = "Age")
```

# Raw Data (imputed)

## Laboratory Measurements

```{r histograms_labs, results = "asis", message = FALSE, warning = FALSE}
labv <- sort(grep("_[SECQ]$", colnames(imp_data), value = TRUE))

for (v in labv) {
    cat("\n\n##", v , "\n\n")
    .hist(imp_data[[v]], main = paste0("Histogram of ", v), xlab = v)
}
```
